### 2016-08-04 plosOneJordanousKeller/responseToReviewers.txt

PONE-D-16-09839
Creativity is what we say it is: identifying key components of creativity
PLOS ONE

We send our thanks to the reviewers and editor for their useful and constructive comments, and appreciate the time they have taken.

@@

Please find our revised version of the manuscript, where we have addressed all concerns of the Reviewers. We have indicated in this accompanying letter the places of the manuscript which were changed as the response of each Reviewers’ remark.

In our submission, we include a clean revised manuscript, this response letter, and a marked-up copy of the changes made from the previous article file as a 'Revised Manuscript with Track Changes' file. We have highlighted changes in the new document using LaTeX strikethrough for removed text and bold font for added text.

>> While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files. PACE helps users ensure that their figures meet PLOS requirements and that the quality of published figures will be as high as possible.

This has been done.

@@

We are very grateful for the feedback from the first reviewer. We agree that the point of the work is not to provide a definition at all, but to present an approach to a model of creativity. We are particularly pleased that the reviewer feels that there is merit in the general approach and that the proposed model is something that other scholars and practitioners would share. This was a very helpful and informative comment and has helped us to reframe the paper in terms of developing a model of creativity.

Thank you to the reviewer also for pointing us at Vartanian (2014) which is very relevant to the current work: we have added a citation in the Background section (lines no 123-126 in the Tracked Changes manuscript). The title has been amended to reflect the reframing and we have carefully edited the text throughout to ensure that the emphasis on modelling rather than definition is clear. The abstract and introductory sections have been reframed accordingly, in particular the Background section. The resulting changes mean that the paper provides a clearer account of the work, and a contribution towards understanding what processes and concepts relevant to creativity are 'sufficiently important to warrant study' based on 'an accumulation of the body of work on creativity to date' (Vartanian 2014).

@@

We have edited the figure accordingly, thank you for this feedback. Regarding the raised concern: we have added a diagram representing the disciplinary makeup of the corpus, as categorised by the journal disciplinary classification in Scopus. Additionally, we have commented on the disciplinary coverage as part of the added text in the Methods section, which give a detailed report and discussion of our search strategy and methods for compiling the corpus.

>> I would suggest that the authors exaggerate the extent to which scholars differ in their view of what constitutes creativity (see p. 5). Completely unanimous agreement on anything in psychology is rare but it seems to me there is pretty unanimous agreement that creativity be defined in terms of (1) new/original and (2) useful/aesthetically appealing, or some variant of these. The authors’ approach still makes an interesting and provocative contribution even if there is widespread agreement on what creativity is.

We have substantially edited the review of scholarly opinions on what constitutes creativity, in response to both reviewers' comments on this point. In particular, we have made several edits to the Background section, as indicated by the markup.

We note in lines 208-213 of the Tracked Changes Manuscript that although originality and usefulness are indeed widely agreed to be two necessary components of creativity, there are many other components which have arisen in previous analyses which contribute to the understanding of creativity, such as Gabora et al's identification of internal cognitive changes.

In particular, in our experience, computational modelling of creativity has shown that it is not sufficient to incorporate only novelty and usefulness in software that is designed to be creative; this overlooks the more subtle aspects of creativity that creativity researchers and practitioners have been aware of for some time.

### 2016-08-04 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
boldening the Appendices as they are a change to the manuscript

\subsection*{S1 Appendix}\label{S1_Appendix}
{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:

@@

\subsection*{S2 Appendix}\label{S2_Appendix}
\bf{Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:

>>>>

\subsection*{S1 Appendix}\label{S1_Appendix}
\bf{Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:

@@

\subsection*{S2 Appendix}\label{S2_Appendix}
{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
